Synthesis report - found all samples

### 2020-02-27 analysis/reports/found_all.Rmd
add fia small

```{r nparts classification}

all_di <-  mutate(all_di, more_than_10 = log_nparts >= 10)
ggplot(filter(all_di, !singletons), aes(x = log(s0), y = log(n0), color = more_than_10)) +
  geom_point() +
  theme_bw()

@@

```{r nparts and dat, fig.dim = c(15,15)}
for(i in 1:nrow(all_di)) {
  if(as.numeric(levels(all_di$nparts_binned)[as.numeric(all_di$nparts_binned[i])]) >= 50) {
    all_di$nparts_binned[i] <- 50
  }
}

>>>>

```{r nparts classification, fig.dim = c(10, 5)}

all_di <-  mutate(all_di, more_than_10 = log_nparts >= 10)
ggplot(filter(all_di, !singletons), aes(x = log(s0), y = log(n0), color = dat)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_d() +
  facet_wrap(vars(more_than_10), scales = "fixed") +
  theme(legend.position = "top")

@@

```{r nparts and dat, fig.dim = c(15,15), include = F}
for(i in 1:nrow(all_di)) {
  if(as.numeric(levels(all_di$nparts_binned)[as.numeric(all_di$nparts_binned[i])]) >= 50) {
    all_di$nparts_binned[i] <- 50
  }
}
